Guarded Recursion in Agda via Sized Types

### 2019-01-29 code-oneclock-paper/latex/paper.tex
polished Section 5.1

Next we give a categorical semantics for the calculus introduced in
\Cref{sec:syntax}.  We take inspiration from M{\o}gelberg's model
\cite{Mogelberg14}, where a (simple) type in a clock context
containing $n$ clocks is interpreted
as a presheaf in $\Set^{(\omega^n)^{\text{op}}}$, where $\omega$ is
the preorder of ordered natural numbers. In our model we replace the
category $\omega$ with the preorder of sizes. Moreover we only
consider the cases where either the clock context is empty or it
contains exactly one clock. This means that a type in \GTT\ is either
interpreted as an element of \F{Set} or as a presheaf over \F{Size}. 
In this section we show how to implement presheaves and how to model
the fragment of \GTT\ corresponding to simply typed lambda
calculus. The interpretation of the guarded recursive and coinductive
features of \GTT\ is given in Section \ref{sec:guarded}.
%% interpreted a $n = 0$ or $n = 1$. where Since in \GTT\
%% every 
%% consider clock contexts containing at most one clock.
%% The type
%% \AD{ClockCtx}  of syntactic clock contexts is also used for semantic clock contexts.
%% 
%% 
%% 
%% a variation of the topos of
%% trees, where as the indexing category we replace the category of
%% ordered natural numbers with the preorder of sizes.
%% 
%% he similar to To do so, we use a similar method as used by M{\o}gelberg \cite{Mogelberg14}.
%% The interpretation of types depend on the clock contexts.
%% If the clock context is empty, then types become sets.
%% If the clock context has one clock, then types are interpreted as objects in the topos of trees.

@@

\section{Modelling Guarded Recursion}
\label{sec:guarded}
Now we have the simple type formers and their terms.
The next step is to add the type formers required for guarded recursion.
We start by defining clock quantification and the later modality, and how to construct terms of those types.
With this in place, we define the fixpoint combinator.
In the end, we give the type former for guarded recursive types.

\subsection{Context Weakening and Clock Quantification}
\input{CloTT/TypeFormers/WeakenClock}
\input{CloTT/TypeFormers/ClockQuantification}

>>>>

Next we give a categorical semantics for the calculus introduced in
\Cref{sec:syntax}.  We take inspiration from M{\o}gelberg's model
\cite{Mogelberg14} in which a (simple) type in a clock context
containing $n$ clocks is interpreted
as a presheaf in $\Set^{(\omega^n)^{\text{op}}}$, where $\omega$ is
the preorder of ordered natural numbers. In our model we replace the
category $\omega$ with the preorder of sizes. Moreover we only
consider the cases where either the clock context is empty or it
contains exactly one clock. This means that a type in \GTT\ is either
interpreted as an element of \F{Set} or as a presheaf over \F{Size}. 
In this section we show how to implement presheaves and how to model
the fragment of \GTT\ corresponding to simply typed lambda
calculus. The interpretation of the guarded recursive and coinductive
features of \GTT\ is given in Section \ref{sec:guarded}.
%% interpreted a $n = 0$ or $n = 1$. where Since in \GTT\
%% every 
%% consider clock contexts containing at most one clock.
%% The type
%% \AD{ClockCtx}  of syntactic clock contexts is also used for semantic clock contexts.
%% 
%% 
%% 
%% a variation of the topos of
%% trees, where as the indexing category we replace the category of
%% ordered natural numbers with the preorder of sizes.
%% 
%% he similar to To do so, we use a similar method as used by M{\o}gelberg \cite{Mogelberg14}.
%% The interpretation of types depend on the clock contexts.
%% If the clock context is empty, then types become sets.
%% If the clock context has one clock, then types are interpreted as objects in the topos of trees.

@@

\section{Modelling Guarded Recursion}
\label{sec:guarded}
In this section we add the guarded
recursive and coinductive features to the denotational semantics.
%Now we have the simple type formers and their terms.
%The next step is to add the type formers required for guarded recursion.
We start by defining the semantic box modality together with its
introduction and elimination rule. Then we construct the semantic
later modality. We show how to define the fixpoint combinator and the
force operation using sized types. In the end we discuss how to model
guarded recursive types.
%% introduce the
%% semantic 
%%  together with the
%% terms associated 
%% and how to construct terms of those types.
%% With this in place, we define the fixpoint combinator.
%% In the end, we give the type former for guarded recursive types.

\subsection{Context Weakening and the Box Modality}
\input{CloTT/TypeFormers/WeakenClock}
\input{CloTT/TypeFormers/ClockQuantification}
